Random Matrix Theory Tools for the Analysis of Functional Magnetic Resonance Imaging Examinations

### 2022-10-20 paper/paper/SPIE/article.tex
wip

\author[a]{Derek Berger}
\author[a]{Jacob Levman}
\author[b]{Gurpreet M. Matharoo}
\affil[a]{St. Francis Xavier University, Department of Computer Science, 4130 University Avenue, Antigonish, Canada, B2G 2W5}
\affil[b]{St. Francis Xavier University, ACENET, 4130 University Avenue, Antigonish, Canada, B2G 2W5}

@@

% Conclusions
% Predictive modeling of lumbar spine surgery outcomes was improved by incorporation of
% image-based features compared to analysis based on conventional demographic data. The SpineCloud
% framework could improve understanding of factors underlying outcome variability and warrants
% further investigation and validation in a larger patient cohort.
\begin{abstract}
\section*{Purpose}
Random matrix theory (RMT) is increasingly becoming a useful tool for understanding complex systems.
Prior studies have examined functional Magnetic Resonance Imaging (fMRI) images using tools from
RMT, with some success. However, RMT computations are complex, and sensitive to numerous analytic
choices. We systematically investigate the usefulness of RMT in a variety of fMRI datasets.

@@

\section*{Results}
We find

\section*{Conclusions}
This document shows the required format and appearance of a manuscript prepared for SPIE journals.
It is prepared using LaTeX2e with the class file \texttt{spieman.cls}. Please note that the
following journals require the use of structured abstracts in manuscript submissions:
\textit{Neurophotonics}, the \textit{Journal of Biomedical Optics}, and the \textit{Journal of
Medical Imaging}. Structured abstracts are encouraged for the \textit{Journal of
Micro/Nanolithography, MEMS, and MOEMS}. Guidelines are available on the journal website. Whether
structured or single-paragraph, the abstract should be a summary of the paper and not an
introduction. Because the abstract may be used in abstracting and indexing databases, it should be
self-contained (i.e., no numerical references) and substantive in nature, presenting concisely the
objectives, methodology used, results obtained, and their significance. A list of up to six keywords
should immediately follow.
\end{abstract}

% Include a list of up to six keywords after the abstract
\keywords{optics, photonics, light, lasers, journal manuscripts, LaTeX template}

% Include email contact information for corresponding author
{\noindent \footnotesize\textbf{*}Fourth author name,  \linkable{myemail@university.edu} }

>>>>

\author[a]{Derek Berger}
\author[a,*]{Jacob Levman}
\author[b]{Gurpreet M. Matharoo}
\affil[a]{St. Francis Xavier University, Department of Computer Science, 4130 University Avenue, Antigonish, Canada, B2G 2W5}
\affil[b]{St. Francis Xavier University, ACENET, 4130 University Avenue, Antigonish, Canada, B2G 2W5}

@@

% Conclusions Predictive modeling of lumbar spine surgery outcomes was improved by incorporation of
% image-based features compared to analysis based on conventional demographic data. The SpineCloud
% framework could improve understanding of factors underlying outcome variability and warrants
% further investigation and validation in a larger patient cohort.
\begin{abstract}

\section*{Purpose}
Random matrix theory (RMT) is an increasingly useful tool for understanding large, complex systems.
Prior studies have examined functional Magnetic Resonance Imaging (fMRI) images using tools from
RMT, with some success. However, RMT computations are complex, and sensitive to numerous analytic
choices, and previous investigations have been mostly explanatory / descriptive. We systematically
investigate the usefulness of RMT in a variety of fMRI datasets in a predictive framework.

@@

\section*{Results}
We find eiegenfeatures to be broadly predictive in a wide variety of contexts, and that RMT-specific
features like the spectral rigidity and level number variance have considerable potential in
feature-engineering for fMRI. On median, we find ...

\section*{Conclusions}
Use RMT yo.

% This document shows the required format and appearance of a manuscript prepared for SPIE journals.
% It is prepared using LaTeX2e with the class file \texttt{spieman.cls}. Please note that the
% following journals require the use of structured abstracts in manuscript submissions:
% \textit{Neurophotonics}, the \textit{Journal of Biomedical Optics}, and the \textit{Journal of
% Medical Imaging}. Structured abstracts are encouraged for the \textit{Journal of
% Micro/Nanolithography, MEMS, and MOEMS}. Guidelines are available on the journal website. Whether
% structured or single-paragraph, the abstract should be a summary of the paper and not an
% introduction. Because the abstract may be used in abstracting and indexing databases, it should be
% self-contained (i.e., no numerical references) and substantive in nature, presenting concisely the
% objectives, methodology used, results obtained, and their significance. A list of up to six keywords
% should immediately follow.
\end{abstract}

% Include a list of up to six keywords after the abstract
\keywords{random matrix, spectral rigidity, level number variance, fMRI, classification, machine-learning}

% Include email contact information for corresponding author
{\noindent \footnotesize\textbf{*}Jacob Levman,  \linkable{jlevman@stfx.ca} }
